Location of Tuna farms

### 2021-06-11 analysis/match_data_sources.Rmd
pushing latest changes to the map!

all_farms <- readRDS("data/all_modeled_marine_farms.rds") %>%
  left_join(all_farms_to_place) %>%
    mutate(data_type = case_when(
    source == "real" ~ "known location", 
    source == "modeled" & estimated == 0 ~ "modeled location, known number of farms",
    source == "modeled" & estimated == 1 ~ "modeled location, estimated number of farms"
  ))

@@

@@

## Now save this as a csv
st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources.csv", layer_options = "GEOMETRY=AS_XY")

>>>>

all_farms <- readRDS("data/all_modeled_marine_farms.rds") %>%
  left_join(all_farms_to_place) %>%
    mutate(data_type = case_when(
    source == "real" ~ "known location", 
    source == "modeled" & estimated == 0 ~ "modeled location, known number of farms",
    source == "modeled" & estimated == 1 ~ "modeled location, estimated number of farms"
  )) %>%
  mutate(estimated = ifelse(is.na(estimated), 0, estimated))

@@

test <- all_farms %>%
  dplyr::filter(is.na(estimated))

@@

## Now save this as a csv
st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources.csv", layer_options = "GEOMETRY=AS_XY", delete_dsn = TRUE)

### 2021-06-11 analysis/paper_figs.Rmd
pushing latest changes to the map!

## Make finer resolution maps (Figure 2)
```{r}
## zoomed maps

@@

(chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

>>>>

## Make finer resolution maps (Figure 2)
```{r}
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)
library(ggpubr)
library(RColorBrewer)
library(ggspatial)
library(ggplot2)
library(patchwork)

## zoomed maps

@@

# (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

### 2021-06-11 archive/marine_mapping_OLD_v1/salmon/food_pressures/salmon_disturbance/STEP1_salmon_tonnes_to_livestock_conversion.Rmd
pushing latest changes to the map!

### Norwegian Fisheries Directorate data wrangling
First we're going to read in the production data we have, and keep all the years. 
```{r wrangling production data}
nor_prod <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/norway_mariculture_gf.csv")) %>% 
  filter(species == "Salmon") %>% 
  dplyr:: select(year, region,variable, value) %>% 
  spread(variable, value) %>% 
  rename(salmon_tonnes = tonnes_fish) %>% 
  mutate(Stock_Jan1_count = Stock_Jan1_count*1000,
         loss_count = loss_count*1000,
         stock_dec_31_count = stock_dec_31_count*1000,
         delivered_for_sale_count = delivered_for_sale_count*1000,
         supplies_count = supplies_count*1000)

>>>>

### Norwegian Fisheries Directorate data wrangling
First we're going to read in the production data we have, and keep all the years. 
```{r wrangling production data}
nor_prod <- read_csv(here("marine/salmon/salmon_farm/data/norway_mariculture_gf.csv")) %>% 
  filter(species == "Salmon") %>% 
  dplyr:: select(year, region,variable, value) %>% 
  spread(variable, value) %>% 
  rename(salmon_tonnes = tonnes_fish) %>% 
  mutate(Stock_Jan1_count = Stock_Jan1_count*1000,
         loss_count = loss_count*1000,
         stock_dec_31_count = stock_dec_31_count*1000,
         delivered_for_sale_count = delivered_for_sale_count*1000,
         supplies_count = supplies_count*1000)

### 2021-06-11 archive/marine_mapping_OLD_v1/tuna/tuna_farms/STEP1_fao_tuna_production.Rmd
pushing latest changes to the map!

 explore <- read_csv(here("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production))*100, 2))
 sum(explore$fao_tonnes_production) # 37072.56
 unique(explore$country) # 7 countries 
```

```{r}
## write out bivalve taxa and production for Juliette
fao_tuna_taxa_prod <- fao %>%
  filter(species %in% tuna_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  group_by(country, year) %>%
  summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  filter(year == 2017)

sum(fao_tuna_taxa_prod$value) # 37072.56

unique(fao_tuna_taxa_prod$country) # 16 countries 
```

>>>>

 explore <- read_csv(here("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production))*100, 2))
```

### 2021-06-11 archive/marine_mapping_OLD_v1/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
pushing latest changes to the map!

Now we will map the remaining countries with shrimp farms. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are not exact locations or comprehensive locations, find the number of farms. 
 - If there is no information at all, note it. We will gapfill later.

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).

5: Comprehensive number of exact farms

4: Subset of exact locations, need to add a specific number of farms to existing locations. 
  - country|species|farm locations
  - country|species|additional points

3: A specific number of farms are known, but no locations 
 - country|species|additional points

2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
 - country, species, n_existing_points

2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.

1: No information on number of farms at all. Need to be gapfilled by tonnage. 
 - country|species|# additional farms (this will be NA)

@@

 - Comprehensive

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 5)

 write_csv(farms_eu_final, here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5/farms_ESP_MLT.csv"))

@@

@@

Croatia: 
Need to add 14 points to existing 1 (a final total of 15 points)

Current data is from NASO maps collection and is only a subset of farms

NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/

We need to add 14 farms to match the total listed by this government source: 
Lukin, A., 2014. Spatial Planning For Marine Aquaculture, Croatia, Zadar County Case. Croatian Ministry of Agriculture, Directorate of Fisheries.

Turkey:
Need to add 5 points to existing 3 (a final total of 8 points)

Data is from NASO maps collection, so only a subset

However the FAO gives us specific numbers 
 - http://www.fao.org/fishery/countrysector/naso_turkey/en
 - 8 farms

@@

farms_med <- data.frame(do.call(rbind, st_geometry(med_pts_latlon)))
names(farms_med) <- c("lon", "lat")
farms_med <- farms_med %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "Croatia", "HRV", "TUR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 4)

write_csv(farms_med, here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5/farms_hrv_tur.csv"))

@@

mapview(farms_med)

#### Croatia
## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
hrv_additional <- data.frame(iso3c = "HRV", type = "tuna", num_additional_farms = 14, data_quality = 4, total_farms = 15)
write.csv(hrv_additional, here("marine/tuna/tuna_farms/data/subset_known_add_points_4/add_farms_hrv.csv"), row.names = FALSE)

#### Turkey 
tur_additional <- data.frame(iso3c = "TUR", type = "tuna", num_additional_farms = 5, data_quality = 4, total_farms = 8)
write.csv(tur_additional, here("marine/tuna/tuna_farms/data/subset_known_add_points_4/add_farms_tur.csv"), row.names = FALSE)

@@

for(i in 2:seq_along(tuna_links)){

  # i = 1
# Read the webpage into R
webpage <- read_html(tuna_links[i])

@@

## unlist the list to get our coordinates 
lat_lon_final <- coords_list %>%
    bind_rows() %>%
  mutate(lat = -lat) %>% ## change lat to have a negative in front of it (because it S)
  mutate(iso3c = "AUS") %>%
  mutate(data_quality = 5) 
## now that we have coordinates, place them on a map and save

@@

write_csv(lat_lon_final, here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5/farms_AUS.csv"))
```

@@

```{r}
farms_jpn <- data.frame(iso3c = "JPN", type = "tuna", num_additional_farms = 92, data_quality = 3)

write_csv(farms_jpn, here("marine/tuna/tuna_farms/data/known_number_farms_3/farms_jpn.csv"))
```

@@

farms_mex <- data.frame(lat = c(31.972882899404116, 31.96836856413186, 31.963417102445995, 31.95861101663323, 31.955698114940013, 31.952930772763118, 31.95030900327055, 31.945939221180044, 31.932974311561416, 31.929769220541903, 31.95016334721594, 31.959630510399904, 31.96764042474878),
                          lon = c(-116.81987407899483, -116.8094027351974, -116.80339458711688, -116.7956698252991, -116.79343822744065, -116.79000499996607, -116.78777340210759, -116.78193691540082, -116.77575710594658, -116.77180889435084, -116.77060726473474, -116.78262356089573, -116.79395321156183), 
                          iso3c = "MEX") %>%
  mutate(data_quality = 5)

@@

write_csv(farms_mex, here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5/farms_MEX.csv"))

@@

```{r}
farm_files <- list.files(here::here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality)

>>>>

Now we will map the remaining countries with tuna farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

 write_csv(farms_eu_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_ESP_MLT.csv"))

@@

 - It says both Tuna and Finfish, but we'll assume Croatia and Turkey are tuna...

@@

@@

farms_med <- data.frame(do.call(rbind, st_geometry(med_pts_latlon)))
names(farms_med) <- c("lon", "lat")
farms_med <- farms_med %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "Croatia", "HRV", "TUR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_med, here("marine/tuna/tuna_farms/data/tuna_sites/farms_hrv_tur.csv"))

@@

mapview(farms_med)
```

@@

for(i in seq_along(tuna_links)){

  # i = 2
# Read the webpage into R
webpage <- read_html(tuna_links[i])

@@

## unlist the list to get our coordinates 
lat_lon_final <- coords_list %>%
    bind_rows() %>%
  mutate(lat = -lat) %>% ## change lat to have a negative in front of it (because it S)
  mutate(iso3c = "AUS") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")
## now that we have coordinates, place them on a map and save

@@

write_csv(lat_lon_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_AUS.csv"))
```

@@

```{r}
world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
plot(world)

japan <- ne_countries(scale = 10, country = "Japan", returnclass = "sf")

#info of our spatial vector object
japan
mapview(japan)
plot(japan)

world <- st_as_sf(world)

japan_world_crs <- st_transform(japan, crs(world))

japan_world_crop <- st_crop(world, japan_world_crs)

japan_world_crop <- japan_world_crop[-c(2,3,4), ]
plot(japan_world_crop)
mapview(japan_world_crop)

j_meters <- st_transform(japan_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(j_meters)

buff <- st_buffer(j_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(japan_world_crop))

japan <- ne_countries(scale = 10, country = "Japan", returnclass = "sf")

linestring_fix <- st_difference(buffer_outline_fixed, japan) ## now grab only the outline 
mapview(linestring_fix)

japan_crop <- as(buffer_outline_fixed, "Spatial")

japan_points_lines <- sample.line(japan_crop, n = 190) ## equally place the number of farms along the coastline 
class(japan_points_lines)
plot(japan_points_lines)

japan_points <- st_as_sf(japan_points_lines) %>%
  mutate(new_id = 1:190) %>%
  filter(!(new_id %in% c(2, 95, 73, 67, 62, 56, 48, 47, 33,  32, 31, 29, 23, 12, 9,  93:112, 116, 118, 121, 123:126, 129:140, 124:145, 148:167, 171:174, 176, 178:190)))
mapview(japan_points)

## now prep dataframe for lat lon points
jpn_pts <- st_centroid(japan_points)

jpn_pts_latlon <- st_transform(jpn_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_jpn <- data.frame(do.call(rbind, st_geometry(jpn_pts_latlon)))
names(farms_jpn) <- c("lon", "lat")

farms_jpn_final <- farms_jpn %>%
  mutate(iso3c = "JPN") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

## visualize it 
farms_jpn <-  st_as_sf(farms_jpn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_jpn)

## write to farms folder 
write_csv(farms_jpn_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_jpn.csv"))
```

@@

farms_mex <- data.frame(lat = c(31.972882899404116, 31.96836856413186, 31.963417102445995, 31.95861101663323, 31.955698114940013, 31.952930772763118, 31.95030900327055, 31.945939221180044, 31.932974311561416, 31.929769220541903, 31.95016334721594, 31.959630510399904, 31.96764042474878),
                          lon = c(-116.81987407899483, -116.8094027351974, -116.80339458711688, -116.7956698252991, -116.79343822744065, -116.79000499996607, -116.78777340210759, -116.78193691540082, -116.77575710594658, -116.77180889435084, -116.77060726473474, -116.78262356089573, -116.79395321156183), 
                          iso3c = "MEX") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

write_csv(farms_mex, here("marine/tuna/tuna_farms/data/tuna_sites/farms_MEX.csv"))

@@

```{r}
farm_files <- list.files(here::here("marine/tuna/tuna_farms/data/tuna_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality, -action_needed)
